The zoon R package for reproducible and shareable species distribution modelling

### 2017-01-17 ms.Rmd
Remove more references to USA in armadillo analysis.

#### Example 1. Modelling the potential distribution of nine-banded armadillo in the USA

@Feng2015 constructed a MaxEnt species distribution model for nine-banded armadillo in the USA using presence-only data on the species' current distribution, and the bioclim [@Hijmans2005] set of environmental correlates.
This model was then used to predict areas in the Americas which may be suitable for the species to become established.

>>>>

#### Example 1. Modelling the potential distribution of nine-banded armadillo

@Feng2015 constructed a MaxEnt species distribution model for nine-banded armadillo using presence-only data on the species' current distribution, and the bioclim [@Hijmans2005] set of environmental correlates.
This model was then used to predict areas in the Americas which may be suitable for the species to become established.
